---
title: | 
 | Employment Imputation Report:
 | `r paste(country_input, '-', OC2_input)`
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(dpi = 72, fig.asp = 0.75, fig.width = 12.638, fig.retina = 1, fig.align = "left")
```

# {.tabset .tabset-pills}

## Pre-imputation {.tabset}

### Current estimates

```{r existing_estimates, echo = FALSE, message = FALSE, warning = FALSE}

theme_update(text = element_text(size = 15))

# Save current estimates chart

data_viz(data = FM_exisiting_estimates, countryinput = country_input, OC2input = OC2_input, title = "Visualization of current estimates")

```

### Subseries table

```{r subseries_table, echo = FALSE, results = 'asis', message = FALSE}

library(knitr)
library(kableExtra)

options(knitr.kable.NA = '')
kable(subseries_table, caption =  "Subseries table of official data", format.args = list(big.mark = " ",
  scientific = FALSE)) %>%
  column_spec(1, bold = T, width_min = "3.2in") %>% 
  column_spec(2:ncol(subseries_table), width_min = "1in") %>% 
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  scroll_box(width = "1000px")

```

## Imputation {.tabset}

```{r imputation_type, echo = FALSE, message = FALSE}

paste("Imputation type: ", imputation_type)

```

### Linear regression

#### Summary plots

```{r reg_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(reg_estimates_disag > 0)) {

# Linear regression summary plots

if (country_input %in% OECD_countries & OC2_input == "Marine fishing") {

reg_variables_viz_fleet(regdata = reg_data, startyear = start_year, endyear = end_year, OC2input = OC2_input, countryinput = country_input)

} else reg_variables_viz(regdata = reg_data, startyear = start_year, endyear = end_year, OC2input = OC2_input, countryinput = country_input)

}

```

#### Regression results

```{r reg_imputation_results, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(reg_estimates_disag > 0)) {

# Regression results

stargazer(reg_result,  type = "html", title = "Results of linear models", align = TRUE, single.row = TRUE, notes="<span>&#42;&#42;&#42;</span>: p<0.01; <span>&#42;&#42;</span>: p<0.05; <span>&#42;</span>: p<0.1", notes.append=F) 
  
}

```

#### Fit of LM over data

```{r reg_imputation_fit, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(reg_estimates_disag > 0)) {

# Visualize fit of LM over data

if (reg_type == 1) {

reg_fit_viz(regdata = reg_data, bestfit = best_fit_LM, startyear = start_year, endyear = end_year, countryinput = country_input, OC2input = OC2_input, best_R2 = best_fit_LM_R2) 

} else if (reg_type == 2) {

reg_fit_viz_manual(regdata = reg_data, startyear = start_year, endyear = end_year, countryinput = country_input, OC2input = OC2_input, best_R2 = best_fit_LM_R2)

}

}

```

#### Disaggregated estimates

```{r reg_imputation_disag, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(reg_estimates_disag > 0)) {

estimator_viz(method = "reg", estimator = "linear regression", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)
   
}

```

### Polynomial trend

```{r trend_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(trend_estimates_disag > 0)) {
    
  # Show a plot of the fitted trend and the data
  
  trend_fit_viz(trenddata = trend_predictions_agg, startyear = start_year, endyear = end_year, countryinput = country_input, OC2input = OC2_input)
  
  estimator_viz(method = "trend", estimator = "polynomial regression", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)
   
}

```

### Linear interpolation

```{r linearint_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(linearint_estimates_disag > 0)) {

estimator_viz(method = "linearint", estimator = "linear interpolation", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)

}

```

### Historical average

```{r histavg_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(histavg_estimates_disag > 0)) {

estimator_viz(method = "histavg", estimator = "historical average", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)

}

```

### Historical growth

```{r histgrowth_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(histgrowth_estimates_disag > 0)) {

estimator_viz(method = "histgrowth", estimator = "historical growth", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)

}

```

### Backwards dragged

```{r bdragged_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(bdragged_estimates_disag > 0)) {

estimator_viz(method = "bdragged", estimator = "backward dragged", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)

}

```

### Forwards dragged

```{r fdragged_imputation, echo = FALSE, message = FALSE, message = FALSE, warning = FALSE, eval = imputation_type == "Aggregated imputation"}

if (nrow(fdragged_estimates_disag > 0)) {

estimator_viz(method = "fdragged", estimator = "forward dragged", dataset = final_estimates, countryinput = country_input, OC2input = OC2_input)

}

```

## Post-imputation {.tabset .active}

### Final estimates

```{r imputed_estimates, echo = FALSE, message = FALSE, warning = FALSE}

data_viz(data = imputed_data, countryinput = country_input, OC2input = OC2_input, title = "Visualization of final imputed data")

```

### Production and productivity

```{r imputed_prod, echo = FALSE, message = FALSE, warning = FALSE}

if (OC2_input == "Aquaculture" | OC2_input == "Marine fishing" | OC2_input == "Inland fishing") {
 
print(ggplot(productivity_imputed, aes(x = year, y = prod_value, group = 1)) + 
  geom_line() +
  labs(title = paste("Visualization of production"), 
       subtitle = paste(OC2_input, "|", country_input), 
       y = "Tonnes",
       x = "Year") +
  scale_y_continuous(labels = addUnits) + 
  scale_x_continuous(breaks = integer_breaks()) +
  theme(aspect.ratio = 3/4))

print(ggplot(left_join(productivity_imputed, productivity_existing, by = "year") %>%
         rename(productivity_imputed = productivity.x, productivity_existing = productivity.y) %>%
         select(year, productivity_imputed, productivity_existing) %>%
         pivot_longer(c(productivity_imputed, productivity_existing), names_to = "variable", values_to = "value")
       , aes(x = year, y = value, group = 1)) + 
  geom_point(aes(color = variable), alpha = 0.5, size = 2) +
  labs(title = paste("Visualization of productivity"), 
       subtitle = paste(OC2_input, "|", country_input), 
       y = "Tonnes/person",
       x = "Year") +
  scale_y_continuous(labels = addUnits) + 
  scale_x_continuous(breaks = integer_breaks()) +
  theme(aspect.ratio = 3/4))
   
}

```

### Comparison table

```{r comparison_table, echo = FALSE, results = 'asis', message = FALSE}

# Create comparison table between original data and processed data

ctable = compare_df(imputed_data %>%
                      select(geographic_area:comment) %>%
                      arrange(geographic_area, year, OC2, OC3, working_time, sex), 
                    FM_exisiting_estimates %>% 
                      select(geographic_area, OC2, OC3, working_time, sex, year, value, flag, comment) %>%
                      arrange(geographic_area, year, OC2, OC3, working_time, sex), 
                    c("geographic_area", "OC2", "OC3", "working_time", "sex", "year"),
                    stop_on_error = FALSE)

# Output HTML table

create_output_table(
  ctable,
  output_type = "html",
  file_name = NULL,
  limit = 1000)

```